A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-18 tex/body.tex
more

The calculus consists of three sets of rules, given in
\figuresname~\ref{fig:cc-rules} to \ref{fig:split-rule}, corresponding to three
phases. The first phase computes the bidirectional closure of $\Ec$. The second
phase makes inferences based on acyclicity (for \hfill datatypes) and uniqueness
(for codatatypes).
The third phase performs case splitting on constructors for
various terms in $\tEc$, the set of $\Sig$-terms occurring in $\Ec$.
%Following the conventions from~\cite{},
%The derivation rules are given in \relax{guarded assignment form},
%where
%
The rules belonging to a phase have priority over those of the subsequent
phases. Rules are applied until the derivation tree is closed or all leaf nodes
are saturated.

@@

At the end of this phase, $\Ec$ induces an equivalence
relation over $\tEc$ such that two terms $t$ and $u$ are equivalent if and
only if $t \teq u \in \Ec$.
Thus, we can regard $\Ec$ as a set of
equivalence classes of terms. For a term $t \in \tEc$, we write $\ec{t}$ to
denote the equivalence class in $\Ec$ that contains $t$.

>>>>

The calculus consists of three sets of rules, given in
\figuresname~\ref{fig:cc-rules} to \ref{fig:split-rule}, corresponding to three
phases. The first phase computes the bidirectional closure of $\Ec$. The second
phase makes inferences based on acyclicity (for \hfill datatypes) and uniqueness
(for codatatypes).
The third phase performs case splitting on constructors for
various terms occurring in $\Ec$.
%Following the conventions from~\cite{},
%The derivation rules are given in \relax{guarded assignment form},
%where
%
The rules belonging to a phase have priority over those of the subsequent
phases. Rules are applied until the derivation tree is closed or all leaf nodes
are saturated.

@@

At the end of this phase, $\Ec$ induces an equivalence
relation over the set of $\Sig$-terms occurring in $\Ec$,
denoted by $\tEc$, such that two terms $t$ and $u$ are equivalent if and
only if $t \teq u \in \Ec$.
Thus, we can regard $\Ec$ as a set of
equivalence classes of terms. For a term $t \in \tEc$, we write $\ec{t}$ to
denote the equivalence class in $\Ec$ that contains $t$.
